Classifier

### 2019-03-01 Paper/01_build_classification_model.Rmd
Knitted the current version of the 01 file

# Load Packages
```{r}
library(fastrtext)
library(tidyverse)
```

@@

```{r}
file_model <- "Output/models/class_mod_1.dat"
train_data_path <- "Output/clean_data/train_data_1.txt"
test_data_path <- "Output/clean_data/test_data_1.txt"
```

@@

# create a character vector containing the tweets to test without their labels
test_labels_without_prefix <- 
  test_train_data %>% 
  filter(test_train == "test") %>% 
  pull(label)
```

@@

```{r}
# train model
execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))

# load model
model <- load_model(file_model)
```

## Review Model:
We'll want to see how a few of the predictions turned out. 
```{r}
# prediction are returned as a list with words and probabilities
predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
head(predictions, 5)
```

This will help us confirm that our model worked as expected.
```{r}
length(predictions)
length(test_labels_without_prefix)
length(test_data_lines)
```

## Accuracy
Let's look at how accurately the model predicted names
```{r}
# Compute accuracy
mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

@@

The hamming loss is the number of wrong labels over the total number of labels. Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
```{r}
# because there is only one category by observation, hamming loss will be the same
get_hamming_loss(as.list(test_labels_without_prefix), predictions)

# test predictions
predictions <- predict(model, sentences = test_to_write)
print(head(predictions, 5))

# you can get flat list of results when you are retrieving only one label per observation
print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
```

>>>>

# Load Packages
```{r}
# library(fastrtext)
# library(tidyverse)
```

@@

```{r}
# file_model <- "Output/models/class_mod_1.dat"
# train_data_path <- "Output/clean_data/train_data_1.txt"
# test_data_path <- "Output/clean_data/test_data_1.txt"
```

@@

# create a character vector containing the tweets to test without their labels
# test_labels_without_prefix <- 
#   test_train_data %>% 
#   filter(test_train == "test") %>% 
#   pull(label)
```

@@

```{r}
# train model
# execute(commands = c("supervised", "-input", train_data_path, "-output", file_model, "-dim", 20, "-lr", 1, "-epoch", 20, "-wordNgrams", 2, "-verbose", 1))
# 
# # load model
# model <- load_model(file_model)
```

## Review Model:
We'll want to see how a few of the predictions turned out. 
```{r}
# prediction are returned as a list with words and probabilities
# predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
# head(predictions, 5)
```

This will help us confirm that our model worked as expected.
```{r}
# length(predictions)
# length(test_labels_without_prefix)
# length(test_data_lines)
```

## Accuracy
Let's look at how accurately the model predicted names
```{r}
# # Compute accuracy
# mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

@@

The hamming loss is the number of wrong labels over the total number of labels. Hamming loss is most useful when applied to multi-classifiers because when it is done with binary classifiers (such as ours), it is simply equal to 1 - accuracy.
```{r}
# # because there is only one category by observation, hamming loss will be the same
# get_hamming_loss(as.list(test_labels_without_prefix), predictions)
# 
# # test predictions
# predictions <- predict(model, sentences = test_to_write)
# print(head(predictions, 5))
# 
# # you can get flat list of results when you are retrieving only one label per observation
# print(head(predict(model, sentences = test_to_write, simplify = TRUE)))
```
